---
title: "Spatial Ecology in R"
author: Duccio Rocchini
format:
  revealjs:
    self-contained: true
editor: visual
---

# The Professor

## Who am I?

```{r ami, echo=T, eval=T}
# R: Search Duccio Rocchini
```

[Quite a difficult question](https://www.google.com/search?q=duccio+rocchini&rlz=1C5CHFA_enIT1141IT1141&oq=duccio+rocchini+&gs_lcrp=EgZjaHJvbWUyDAgAEEUYORiABBiiBDIGCAEQIxgnMgYIAhAjGCcyBwgDEAAYgAQyBggEEEUYPDIGCAUQRRg8MgYIBhBFGDwyBggHEEUYQdIBCDQzNTFqMGo3qAIAsAIA&sourceid=chrome&ie=UTF-8)

# The course

## Program

[Looking at the page](https://www.unibo.it/en/study/course-units-transferable-skills-moocs/course-unit-catalogue/course-unit/2025/535506)

## Reasoning at three different levels

-   Spatial structure of **populations** and population change in time: introduction to poopulation ecology

-   Spatial structure of **communities**: introduction to community ecology and community monitoring metrics

-   Spatial structure of **ecosystems** and functions: exploring the main ecosystem functions

## Populations \| Point Patterns Analysis

```{r pop, echo=T, eval=T}
library(spatstat)
plot(bei, cex=.2, pch=19)
```

## Populations \| Density maps

```{r popde, echo=T, eval=T}
library(spatstat)
densitymap <- density(bei)
plot(densitymap)
points(bei, cex=.2)
```

## Communities \| Multivariate analysis

```{r comm, echo=T, eval=T}
library(vegan)
data(dune)
multivar <- decorana(dune)
plot(multivar)
```

## Ecosystems

```{r eco, echo=T, eval=T}
library(imageRy)
citation("imageRy")
```

## Using the imageRy package

```{r ima, echo=T, eval=T}
library(terra)
library(imageRy)
m1992 <- im.import("matogrosso_l5_1992219_lrg.jpg")
```

## Multitemporal analysis

```{r multitemp, echo=T, eval=T}
library(terra)
library(imageRy)
m2006 <- im.import("matogrosso_ast_2006209_lrg.jpg")
```

## The book

[R Coding for Ecology](https://link.springer.com/book/9783031996641)

## The code

-   [R](https://www.r-project.org/)
-   [Markdown](https://markdownlivepreview.com/)
-   [Quarto](https://markdownlivepreview.com/)
-   [LaTeX](https://www.latex-project.org/)

## First steps

-   Install [R](https://cran.stat.unipd.it/)
-   Install [RStudio](https://posit.co/download/rstudio-desktop/)

## GitHub account

<https://github.com/ducciorocchini/>

## Artificial intellingence

<https://chatgpt.com/>

# The exam

## Procedure

-   Write a code project in GitHub using MarkDown
-   Present the project during the exam date
